Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-04 PandaOverview.tex
remove addressed comment.
Notes clean-up

\mtnote{Addresses Alexei's comment. I eliminated `event' as abstraction and used
datum/data/physical process when discussing data management in the whole
section.}

PanDA's application model assumes tasks, workloads and workflows. Tasks
represent a set of operations performed on
% a set of events that are
data sets stored in one or more input files. Tasks are decomposed into jobs,
where each job represents the task's set of operations and a partition of the
task's
% events
data set. Since 2005, a certain amount of parallelism has been
progressively introduced for job execution~\cite{crooks2012multi} but, so far,
HEP applications have not required MPI\mtnote{Addresses Alexei's comment. If
this is still too soft, we can write: ``but HEP applications do not require
MPI.''}. Jobs are supposed to be relatively self-contained, capable of setting
up their own execution environment or having a minimal set of common
dependences.

@@

In PanDA's data model, each
% event
datum refers to the recorded or simulated measurement of a physical
% event
process.
% One or more events
Data can be packaged into files or other containers. As with jobs, data
have both attributes and states, and some of the attributes are shared between
events and jobs. Raw, reconstruction, and simulation data are assumed to be
distributed across multiple storage facilities and managed by the ATLAS
Distributed Data Management (DDM)~\cite{garonne2012atlas}. When necessary,
datasets required by each job are assumed to be replicated over the network,
both for input and output data.

@@

\mtnote{From Danila: DDM enacts decisions about registering files into datasets.
These decisions are made by productions. DDM DOES OT DECIDE which file should be
in which dataset.}\mtnote{Done.}
\mtnote{No communication between APF and PanDA Server (deleted arrow, adjust
numbers and related text)}\mtnote{Done.}
\mtnote{No more DDM Service on Edge on grid sites. DDM directly interacts with
SE (deleted arrows, moved number 8. Update labels and related text)}\mtnote{Done.}

@@

When a PanDA Pilot becomes available on a site, it calls the Job Dispatcher
module of the PanDA Server, requesting  a job to execute
(Fig.~\ref{fig:architecture}:11). The Job Dispatcher interrogates the Task
Buffer module for a job that is bound to the site of that pilot and ready to be
executed. Task Buffer checks the global queue (i.e., the PanDA database) and,
upon availability, returns a suitable job to the Job Dispatcher. \jhanote{end of
previous sentence needs some attention}\mtnote{Done.} The Job Dispatcher
dispatches that job to the PanDA Pilot (Fig.~\ref{fig:architecture}:12).

>>>>

% \mtnote{Addresses Alexei's comment. I eliminated `event' as abstraction and used
% datum/data/physical process when discussing data management in the whole
% section.}

% \mtnote{Addresses Alexei's comment. If this is still too soft, we can write:
% ``but HEP applications do not require MPI.''}

PanDA's application model assumes tasks, workloads and workflows. Tasks
represent a set of operations performed on data sets stored in one or more input
files. Tasks are decomposed into jobs, where each job represents the task's set
of operations and a partition of the task's data set. Since 2005, a certain
amount of parallelism has been progressively introduced for job
execution~\cite{crooks2012multi} but, so far, HEP applications have not required
MPI. Jobs are supposed to be relatively self-contained, capable of setting up
their own execution environment or having a minimal set of common dependences.

@@

In PanDA's data model, each datum refers to the recorded or simulated
measurement of a physical process. Data can be packaged into files or other
containers. As with jobs, data have both attributes and states, and some of the
attributes are shared between events and jobs. Raw, reconstruction, and
simulation data are assumed to be distributed across multiple storage facilities
and managed by the ATLAS Distributed Data Management
(DDM)~\cite{garonne2012atlas}. When necessary, datasets required by each job are
assumed to be replicated over the network, both for input and output data.

@@

% \mtnote{From Danila: DDM enacts decisions about registering files into datasets.
% These decisions are made by productions. DDM DOES OT DECIDE which file should be
% in which dataset.}\mtnote{Done.}
% \mtnote{No communication between APF and PanDA Server (deleted arrow, adjust
% numbers and related text)}\mtnote{Done.}
% \mtnote{No more DDM Service on Edge on grid sites. DDM directly interacts with
% SE (deleted arrows, moved number 8. Update labels and related text)}\mtnote{Done.}

@@

When a PanDA Pilot becomes available on a site, it calls the Job Dispatcher
module of the PanDA Server, requesting  a job to execute
(Fig.~\ref{fig:architecture}:11). The Job Dispatcher interrogates the Task
Buffer module for a job that is bound to the site of that pilot and ready to
be executed. Task Buffer checks the global queue (i.e., the PanDA database)
and, upon availability, returns a suitable job to the Job Dispatcher. The Job
Dispatcher dispatches that job to the PanDA Pilot
(Fig.~\ref{fig:architecture}:12).
